Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Merged GLAD/EDGI cohorts together to collapse age retro plot to 3 cohorts

>>>>

###Retro

```{r Merge GLAD/EDGI samples together for plot}

#Merge GLAD and EDGI Samples into one sample

dat.retro <- dat.retro %>% 
  mutate(Sample_plot = 
           case_when(
             dat.retro$Sample == "GLAD" ~ "GLAD/EDGI",
             dat.retro$Sample == "EDGI" ~ "GLAD/EDGI",
             dat.retro$Sample == "NBR" ~ "NBR",
             dat.retro$Sample == "RAMP" ~ "RAMP"
           ))

#Check that it worked

dat.retro %>% 
  group_by(Sample_plot) %>% 
  summarise(N = n())

```{r GLAD/EDGI, NBR and RAMP age}

dat.retro %>% 
  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Age distribution of the retro cohorts",
       subtitle = paste("N =", dim(dat.retro)[1]),
       x = "Age (years)",
       y = "") +
  theme(legend.position = "bottom")
